### 2021-04-21 paper/ase21/conclusion.tex
Revised Sec. 6 & 7

\section{Conclusion}\label{sec:conclusion}
Since an incorrect description in ECMAScript can lead to the wrong JavaScript
engine implementations, checking the correctness of ECMAScript is essential.
Since ECMAScript is annually released and developed in open process, it becomes
more labor-intensive and error-prone.  To alleviate the problem, we propose
$\tool$, a JavaScript Specification Type Analyzer using Refinement.  It is the
first tool that performs \textit{type analysis} on JavaScript specifications and
detects specification bugs using a \textit{bug detector}.  Moreover, to increase
precision of type analysis, we present \textit{condition-based refinement} for
type analysis, which prunes out infeasible abstract states using conditions of
assertions and branches.  We evaluated $\tool$ with all 864 versions in the
official ECMAScript repository for the recent three years from 2018 to 2021.
Our tool took \inred{230} seconds on average to perform type analysis for each
version, and detected \inred{200} type-related specification bugs with
\inred{50.3}\% precision; \inred{91} out of \inred{200} bugs are true bugs.
Among them, \inred{14} bugs are newly detected by $\tool$ and the committee
confirmed all of them.

>>>>

\section{Conclusion}\label{sec:conclusion}
Checking the correctness of ECMAScript is essential because an incorrect description
in ECMAScript can lead to wrong implementations of JavaScript engines. However,
since ECMAScript is annually released and developed in an open process, checking
its correctness becomes more labor-intensive and error-prone.  To alleviate the problem,
we propose $\tool$, a JavaScript Specification Type Analyzer using Refinement.
It is the first tool that performs \textit{type analysis} on JavaScript specifications and
detects specification bugs using a \textit{bug detector}.  We also present
\textit{condition-based refinement} for type analysis, which prunes out infeasible abstract states
using conditions of assertions and branches to improve the analysis precision.
We evaluated $\tool$ with all 864 versions in the official ECMAScript repository
for the last three years from 2018 to 2021.  It took \inred{137.3} seconds on average
to perform type analysis for each version, and detected \inred{161} type-related specification bugs with
\inred{56.5}\% precision; \inred{91} out of \inred{161} reported bugs are true bugs.
Among them, \inred{14} bugs are newly detected by $\tool$, and the
committee confirmed them all.

### 2021-04-21 paper/ase21/related.tex
Revised Sec. 6 & 7

\paragraph{ECMAScript-based Applications}
\begin{itemize}
  \item Engines~\cite{v8, graaljs, qjs, moddable}
  \item Static Analyzer~\cite{safe, tajs, jsai, wala}
  \item Debuggers: JSExplain: A Double Debugger for JavaScript~\cite{jsexplain}
  \item Verification Tool: JaVerT: JavaScript Verification
    Toolchain~\cite{javert}
\end{itemize}

\paragraph{Mechanized Specifications}
\begin{itemize}
  % manual
  \item The Essence of Javascript~\cite{lambdajs}
  \item A Trusted Mechanised JavaScript Specification~\cite{jscert}
  \item KJS: A complete formal semantics of JavaScript~\cite{kjs}

  % automatic
  \item BASESPEC: Comparative Analysis of Baseband Software and Cellular
    Specifications for L3 Protocols~\cite{basespec}
  \item Automatic extraction of x86 formal semantics from its natural
    language description~\cite{x86}
  \item Formal semantics extraction from natural language specifications for
    ARM~\cite{arm}
  \item SpecTest: Specification-Based Compiler Testing~\cite{spectest}
  \item Automatic Model Generation from Documentation for Java API Functions
  \item COMFORT: JS Fuzzer using ECMAScript
  \item JISET: JavaScript IR-based Semantics Extraction Toolchain~\cite{jiset}
\end{itemize}

\paragraph{Correctness of ECMAScript}
\begin{itemize}
  \item JISET: JavaScript IR-based Semantics Extraction Toolchain~\cite{jiset}
  \item JEST: N+1-version Differential Testing of Both JavaScript Engines
    and Specification~\cite{jest}
\end{itemize}

% \begin{itemize}
%   \item Abstract Interpretation~\cite{ai1977, ai1992}
%   \item JISET: JavaScript IR-based Semantics Extraction Toolchain~\cite{jiset}
%   \item JavaScript Manual Mechanized Specification:
%     \begin{itemize}
%       \item The Essence of Javascript~\cite{lambdajs}
%       \item A Trusted Mechanised JavaScript Specification~\cite{jscert}
%       \item JaVerT: JavaScript Verification Toolchain~\cite{javert}
%       \item KJS: A complete formal semantics of JavaScript~\cite{kjs}
%       \item JEST: N+ 1-version Differential Testing of Both JavaScript Engines
%         and Specification~\cite{jest}
%     \end{itemize}
%   \item Automatic Mechanized Specification for others:
%     \begin{itemize}
%       \item Automatic extraction of x86 formal semantics from its natural
%         language description~\cite{x86}
%       \item Formal semantics extraction from natural language specifications for
%         ARM~\cite{arm}
%       \item SpecTest: Specification-Based Compiler Testing~\cite{spectest}
%       \item BASESPEC: Comparative Analysis of Baseband Software and Cellular
%         Specifications for L3 Protocols~\cite{basespec}
%     \end{itemize}
% \end{itemize}

>>>>

Type analysis of JavaScript specifications has three related topics:
JavaScript tools, mechanized specification extraction, and specification-based testing.

\paragraph{JavaScript Tools}
ECMAScript is the standard language specification for JavaScript maintained by
the Ecma Technical Committee 39 (TC39).  In late 2014, the committee announced
its plan to release ECMAScript annually and adopt the open development process
to quickly adapt to evolving development environments.  Various JavaScript engines such
as Google V8~\cite{v8}, GraalJS~\cite{graaljs}, QuickJS~\cite{qjs}, and Moddable
XS~\cite{moddable} should conform to the syntax and semantics described in
annually updated ECMAScript.  Beyond JavaScript engines, diverse
research projects use JavaScript specifications.  The main research direction
has been static analyzers such as JSAI~\cite{jsai}, SAFE~\cite{safe},
TAJS~\cite{tajs}, and WALA~\cite{wala} based on the abstract interpretation
framework~\cite{ai1977, ai1992} with their own analysis techniques.
They defined abstract semantics of the JavaScript semantics described in ECMAScript to statically
analyze JavaScript programs in a finite time.
Chargu{\'e}raud et al.~\cite{jsexplain} presented JSExplain, a debugger for JavaScript, by
implementing a reference interpreter in OCaml following the algorithm steps in ECMAScript closely.
For a given JavaScript program, the debugger interactively produces execution traces
investigated in a browser, with an interface that displays the
JavaScript code and the interpreter's state.
Fragoso Santos et al.~\cite{javert} introduced JaVerT, a JavaScript verification toolchain, based
on the separation logic with an intermediate goto language JSIL.
JaVerT 2.0~\cite{javert2} extends it to support compositional symbolic execution
for JavaScript based on bi-abduction.  However, because all of them manually handle
ECMAScript with their own intermediate representations, most of them still 
target ES5.1 released in 2011 instead of the latest one.

\paragraph{Mechanized Specification Extraction}
Researchers in various application domains have extracted mechanized specifications from
specifications written in natural languages to handle the contents in the specifications automatically.
For system architectures, researchers utilized Natural
Language Processing (NLP) and Machine Learning (ML) techniques to extract formal semantics
of small-sized low-level assembly languages for x86~\cite{x86} and ARM~\cite{arm}.
For Java API functions, Zhai et al.~\cite{javadoc} presented a
technique to automatically extract models from their documentation using NLP techniques.
For the JavaScript programming language, Park et al.~\cite{jiset}
presented $\jiset$, a tool that extracts a mechanized specification from ECMAScript.
While all the previous JavaScript formal semantics~\cite{lambdajs, jscert,
kjs} were manually defined, $\jiset$ automatically extracts formal semantics directly from ECMAScript.
We utilized $\jiset$ to analyze 864 ECMAScript versions via $\tool$.

\paragraph{Specification-based Testing}
Recently, researchers have utilized specifications to test their implementations.
For network protocols, Kim et al.~\cite{basespec} proposed a novel approach named
\textsc{BaseSpec}, which extracts message structures from tables in cellular
specifications for L3 protocols to perform comparative analysis of baseband software.
Schumi and Sun~\cite{spectest} presented SpecTest, which utilized an
executable language semantics to perform fuzzing for Java and Solidity compilers.
For JavaScript, Ye et al.~\cite{comfort} presented \textsc{Comfort}, a
compiler fuzzing framework to detect JavaScript engine bugs using ECMAScript
with deep learning-based language models.
Park et al.~\cite{jest} extended $\jiset$ to $\jest$, which performs $N$+1-version differential testing
with $N$ different JavaScript engines and a reference interpreter extracted from ECMAScript.
$\jest$ detects not only engine bugs but also specification bugs in
ECMAScript using the cross-referencing oracle.  However, it requires multiple JavaScript engines and
takes dozens of hours to test a version of ECMAScript.
Instead, $\tool$ can detect specification bugs without JavaScript engines in less than five minutes.
Because $\tool$ uses abstract semantics while $\jest$ uses concrete semantics,
$\tool$ can quickly analyze more semantics than $\jest$.
